To-Do List

### 2016-01-20 Rmd/biodiversity-layer.Rmd
Many updates as getting ready to assemble and mask inputs

## Prepare impacts layer
```{r, eval = FALSE}
fnms <- full_path(full_path(p_bd, "act_veg"), 
                  dir(full_path(p_bd, "act_veg"), pattern = ".tif$"))
s <- stack(lapply(fnms, function(x) raster(x)))
sm <- mask(s, mgrid)

# Sum for total - the inverse of this will be the farmable areas
remfrac <- calc(s, sum)
remfrac <- mask(remfrac, mgrid)

# Calculate intactness
w <- matrix(nrow = 11, ncol = 11)
w[] <- 1
intact <- focal(remfrac, w = w, fun = mean, na.rm = TRUE)
# intact <- mask(intact, mgrid)
# plot(intact)

@@

# Check the relative areas against histograms from 30 m layer
v <- gdalinfo(vegrem@file@name, hist=TRUE)[31]  # gdalinfo histogram
v <- as.numeric(strsplit(v, " ")[[1]])  # convert to numeric, get numbers
v <- v[!is.na(v)]  # remove NAs
lcvals <- c(0:(length(v) - 1))[which(v != 0)]  # what are the actuals, less 0
hist30 <- cbind(lcvals, v[v != 0])

@@

### Weighting in relation to rarity and protectedness
```{r, eval = TRUE}
# Combine protected areas (NPs and GMAs, forest reserves)
nps$code <- ifelse(nps$TYPE == "gma", 2, 1) 
npsr <- rasterize(nps, mgrid, field = "code")  # rasterize NPs/GMAs
npsr[is.na(npsr)] <- 0  
freserves$code <- 3  
freservesr <- rasterize(freserves, mgrid, field = "code")  # forest reserves
freservesr[is.na(freservesr)] <- 0
pas <- npsr + freservesr  # sum them
reclmat <- cbind(0:5, c(0:3, 1, 2))
pas <- reclassify(pas, reclmat)
pas <- mask(pas, mgrid)
# plot(pas)
# plot(freservesr)

@@

# plots to examine them
labs <- gsub("veg", "", names(wgtsn))
# par(mfrow = c(2, 1), mar = c(2, 2, 2, 2))
# weights against protected proportion (NPs + GMAs)
plot(wgtsn, prop_prot2, pch = "", ylab = "")
text(wgtsn, prop_prot2, labels = labs, cex = 0.75)
# weights against protected proportion (NPs only)
plot(wgtsn, prop_prot1, pch = "", ylab = "")
text(wgtsn, prop_prot1, labels = labs, cex = 0.75)
# additive weights factoring in protected proportion versus protected proportion
plot(wgts_prop2, prop_prot, pch = "", ylab = "")
text(wgts_prop2,  prop_prot, labels = labs, cex = 0.75)
# BD + NP protected proportion versus NP protected proportion
plot(wgts_prop_np, prop_prot1, pch = "", ylab = "")
text(wgts_prop_np,  prop_prot1, labels = labs, cex = 0.75)
# protected proportion weighted versus same but log-transformed
plot(wgts_prop, wgts_propl, pch = "", ylab = "")
text(wgts_prop,  wgts_propl, labels = labs, cex = 0.75)
# Bd weights against BD + protected proportion weights
plot(wgtsn, wgts_prop, pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn, wgts_prop, labels = labs, cex = 0.75)
# Bd weights against BD + NP protected proportion weights
plot(wgtsn, wgts_prop_np, pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn, wgts_prop_np, labels = labs, cex = 0.75)
# Bd weights versus log-transformed BD + protected proportion weights
plot(wgtsn, wgts_propl, pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn,  wgts_propl, labels = labs, cex = 0.75)
# The same but against multiplicative weights
plot(wgtsn, wgtsn * unlist(1 - prop_prot), pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn,  wgtsn * unlist(1 - prop_prot), labels = labs, cex = 0.75)
# sort(wgts_prop); sort(wgts_prop_np)
# sort(wgtsn)

@@

# final biodiversity layer
bdf <- calc(stack(bdr, pafix), max)
plot(remfrac)
plot(bdf)

writeRaster(bdf, file = full_path(p_bd, "bdprior.tif"))

@@

>>>>

## Prepare impacts layer
```{r, eval = FALSE}
vnms <- dir(full_path(p_bd, "act_veg"), pattern = ".tif$")
vnms <- vnms[vnms != "veg88.tif"]  # drop water bodies
fnms <- full_path(full_path(p_bd, "act_veg"), vnms)
s <- stack(lapply(fnms, function(x) raster(x)))
sm <- mask(s, mgrid)

# keep for assessing impacts
writeRaster(sm, filename = full_path(p_bd, "ZA-vegremain.tif"), 
            overwrite = TRUE)

# Sum for total - the inverse of this will be the farmable areas
remfrac <- calc(s, sum)
remfrac <- mask(remfrac, mgrid)
writeRaster(remfrac, filename = full_path(p_bd, "ZA-remfrac.tif"), 
            overwrite = TRUE)

# Calculate intactness
w <- matrix(nrow = 11, ncol = 11)
w[] <- 1
intact <- focal(remfrac, w = w, fun = mean, na.rm = TRUE)
writeRaster(intact, filename = full_path(p_bd, "intactness.tif"), 
            overwrite = TRUE)

# intact <- mask(intact, mgrid)
# plot(intact)

@@

# Check the relative areas against histograms from 30 m layer
v <- gdalinfo(vegrem@file@name, hist=TRUE)[31]  # gdalinfo histogram
v <- as.numeric(strsplit(v, " ")[[1]])  # convert to numeric, get numbers
v <- v[!is.na(v)]  # remove NAs
lcvals <- c(0:(length(v) - 1))[which(v != 0)]  # what are the actuals, less 0
hist30 <- cbind(lcvals, v[v != 0])
hist30 <- hist30[-21, ]  # type 88

@@

### Weighting in relation to rarity and protectedness
```{r, eval = FALSE}
# Combine protected areas (NPs and GMAs, forest reserves)
nps$code <- ifelse(nps$TYPE == "gma", 2, 1) 
npsr <- rasterize(nps, mgrid, field = "code")  # rasterize NPs/GMAs
npsr[is.na(npsr)] <- 0  
freserves$code <- 3  
freservesr <- rasterize(freserves, mgrid, field = "code")  # forest reserves
freservesr[is.na(freservesr)] <- 0
pas <- npsr + freservesr  # sum them
reclmat <- cbind(0:5, c(0:3, 1, 2))
pas <- reclassify(pas, reclmat)
pas <- mask(pas, mgrid)
# plot(pas)
# plot(freservesr)

@@

# plots to examine them
labs <- gsub("veg", "", names(wgtsn))
# par(mfrow = c(2, 1), mar = c(2, 2, 2, 2))
# weights against protected proportion (NPs + GMAs)
plot(wgtsn, prop_prot2, pch = "", ylab = "")
text(wgtsn, prop_prot2, labels = labs, cex = 0.75)
# weights against protected proportion (NPs only)
plot(wgtsn, prop_prot1, pch = "", ylab = "")
text(wgtsn, prop_prot1, labels = labs, cex = 0.75)
# additive weights factoring in protected proportion versus protected proportion
plot(wgts_prop, prop_prot2, pch = "", ylab = "")
text(wgts_prop,  prop_prot2, labels = labs, cex = 0.75)
# BD + NP protected proportion versus NP protected proportion
plot(wgts_prop_np, prop_prot1, pch = "", ylab = "")
text(wgts_prop_np,  prop_prot1, labels = labs, cex = 0.75)
# protected proportion weighted versus same but log-transformed
plot(wgts_prop, wgts_propl, pch = "", ylab = "")
text(wgts_prop,  wgts_propl, labels = labs, cex = 0.75)
# Bd weights against BD + protected proportion weights
plot(wgtsn, wgts_prop, pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn, wgts_prop, labels = labs, cex = 0.75)
# Bd weights against BD + NP protected proportion weights
plot(wgtsn, wgts_prop_np, pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn, wgts_prop_np, labels = labs, cex = 0.75)
# Bd weights versus log-transformed BD + protected proportion weights
plot(wgtsn, wgts_propl, pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn,  wgts_propl, labels = labs, cex = 0.75)
# The same but against multiplicative weights
plot(wgtsn, wgtsn * unlist(1 - prop_prot1), pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn,  wgtsn * unlist(1 - prop_prot1), labels = labs, cex = 0.75)
# sort(wgts_prop); sort(wgts_prop_np)
# sort(wgtsn)

@@

# final biodiversity layer
bdf <- calc(stack(bdr, pafix), max)
# plot(remfrac)
# plot(bdf)

writeRaster(bdf, file = full_path(p_bd, "bdprior.tif"), overwrite = TRUE)
vprops <- cbind("var" = c("area", "rarity", "priority"),
                rbind(vtots / nrow(veg_dt), wgti, data.table(t(wgts_prop_np))))
save(vprops, file = full_path(p_bd, "vprops.rda"))

@@

## Resulting model inputs

`vprops.rda` - table of veg type area, rarity value, and prioritization value

`bdprior.tif` - biodiversity prioritization grid

`ZA-vegremain.tif` - vegetation remaining grid, for assessing conversion impacts

`ZA-remfrac.tif` - to combine with other farmable area masks

### 2016-01-20 Rmd/cost-distance.Rmd
Various scripts for creating terrain, cropland, and actual vegetation layers
Many updates as getting ready to assemble and mask inputs

```{r, eval = FALSE}
library(lmisc)
library(raster)
library(rgdal)
library(rgeos)
library(gdalUtils)
p_root <- set_base_path("zambiaToff")
p_roads <- full_path(p_root, "external/input_devel/roads/")
p_roads2 <- paste0("~/Dropbox/data/zari/infrastructure/zambia/rda_dump/", 
                   "Final Shape files RDA/")
p_trade <- "~/Dropbox/projects/agroEcoTradeoff/external/base_data/"

@@

# Processing cost grid to make it usable by model
```{r, eval = FALSE}
# Some code I use to quickly copy data out of the ArcGIS processing folder
# back to my machine
cnm <- "/Volumes/Data/loMadzala/GIS/Zambia/costdistance/zamcost2.tif"
file.copy(cnm, "cost.tif", overwrite = TRUE)

# read in the cost raster
costr <- raster("cost.tif")

# first we have to cut this down for R, and then convert it to a data.table
# get the zambia mask for AgroEcoTradeoffs
# find your install of AgroEcoTradeoffs
# read in the "ZA-mask.csv" file, which is a data.table
library(agroEcoTradeoff)
dt_path <- "~/Dropbox/projects/agroEcoTradeoff/external/data/dt/"
msk <- fread(paste0(dt_path, "ZA-mask.csv"))  # read it in
mskr <- dt_to_raster(msk, CRSobj = projection(zamr))  # convert to raster

# now crop the cost surface, then resample it to  
# line up with our mask raster, since they are slightly offset from one 
# another, and then mask it
costrcr <- crop(costr, mskr)
costcrrs <- resample(costrcr, mskr)
costrmsk <- mask(costcrrs, mskr)
plot(costrmsk)  # voila

# then convert it to a data.table as follows
costdt <- na.omit(as.data.table(costrmsk, xy = FALSE))

# and then you will write it out as a csv file.  
fnm <- "../../data/ZA-cost.csv"
write.table(costdt, file = fnm, sep = ",", col.names = TRUE, row.names = FALSE)
```

Your final output csv file will want to replace the ZA-cost.csv file in agroEcoTradeoffs folder `external/data/dt`, and then the model will work nicely.

>>>>

```{r, eval = FALSE}
library(lmisc)
library(raster)
library(rgdal)
library(rgeos)
library(gdalUtils)
p_root <- lmisc::set_base_path("zambiaToff")
p_roads <- full_path(p_root, "external/input_devel/roads/")
p_roads2 <- paste0("~/Dropbox/data/zari/infrastructure/zambia/rda_dump/", 
                   "Final Shape files RDA/")
p_trade <- "~/Dropbox/projects/agroEcoTradeoff/external/base_data/"
p_cost <- full_path(p_root, "external/input_devel/roads/cost")

@@

# Processing cost grid to make it usable by model
```{r, eval = FALSE}
# Some code I use to quickly copy data out of the ArcGIS processing folder
# back to my machine
cnm <- "/Volumes/Data/loMadzala/GIS/Zambia/costdistance/zamcost2.tif"
file.copy(cnm, full_path(p_cost, "zamcost.tif"), overwrite = TRUE)

# read in the cost raster
costr <- raster(full_path(p_cost, "zamcost.tif"))

# first we have to cut this down for R, and then convert it to a data.table
# get the zambia mask for AgroEcoTradeoffs
# find your install of AgroEcoTradeoffs
# read in the "ZA-mask.csv" file, which is a data.table
library(agroEcoTradeoff)
# dt_path <- "~/Dropbox/projects/agroEcoTradeoff/external/data/dt/"
# msk <- fread(paste0(dt_path, "ZA-mask.csv"))  # read it in
# mskr <- dt_to_raster(msk, CRSobj = projection(zamr))  # convert to raster
mgrid <- raster(full_path(p_trade, "ZA-grid.tif"))

# now crop the cost surface, then resample it to  
# line up with our mask raster, since they are slightly offset from one 
# another, and then mask it
costrcr <- crop(costr, mgrid)
costcrrs <- resample(costrcr, mgrid)
# costrmsk <- mask(costcrrs, )
# plot(costcrrs)  # voila

writeRaster(costcrrs, filename = full_path(p_cost, "ZA-cost.tif"))

# then convert it to a data.table as follows
# costdt <- na.omit(as.data.table(costrmsk, xy = FALSE))

# and then you will write it out as a csv file.  
# fnm <- "../../data/ZA-cost.csv"
# write.table(costdt, file = fnm, sep = ",", col.names = TRUE, 
#             row.names = FALSE)

## Resulting model inputs

Alistair's project:
Your final output csv file will want to replace the ZA-cost.csv file in agroEcoTradeoffs folder `external/data/dt`, and then the model will work nicely.

Full analysis: 
`ZA-cost.tif` - for masking, etc

### 2016-01-20 Rmd/maize-soy-grid.Rmd
Many updates as getting ready to assemble and mask inputs

Based on simulated potential yields run by Di Tian. 
```{r, eval = FALSE}
library(data.table)
library(lmisc)
library(dtraster)
# devtools::install_github("PrincetonUniversity/lmisc")

p_root <- set_base_path()
p_crop <- "~/Dropbox/data/agricultural/zambia/dssat/"
p_cropmod <- "~/Dropbox/projects/rCropMod/external/ext_data/"
p_agro <- "~/Dropbox/projects/agroEcoTradeoff/external/base_data/"

@@

plot(dt_to_raster(IDr[, .(x, y, as.factor(Zone))], CRS(prj)))
prj <- paste0("+proj=aea +lat_1=20 +lat_2=-23 +lat_0=0 +lon_0=25 +x_0=0 +y_0=0",
              " +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs")
gcs <- "+proj=longlat +datum=WGS84"

@@

# Take average of mean yields across the different cultivar types. 
# This will give 1 set of yields for each of the three management scenarios
# Subsistence, rainfed commercial, irrigated
# The same approach can be used to estimate the average of the 10th percentile 
# across cultivars, or median, or 90th, etc. 
yld_mus <- lapply(crops, function(x) {  # x <- crops[[1]]
  ymu <- lapply(c("S", "R", "I"), function(y) {  #y <- "S"
    cnms <- names(yld_rasts[[x]])[grep(paste0("mu_", y), names(yld_rasts[[x]]))]
    ylds <- copy(yld_rasts[[x]][, c("x", "y", cnms), with = FALSE])
    ylds[, c(x) := round(rowMeans(.SD)), .SDcols = cnms]
    ylds[, c(cnms) := NULL]
    ylds
  })
  named_out(ymu, c("S", "R", "I"))
})
names(yld_mus) <- crops

plot(dt_to_raster(yld_mus[[2]]$R, CRSobj = gcs))
```
<a href="#top">Back to top</a>

# 1 km grids

Average mean yields across cultivars within management treatments, and then reseample to 1 km grids. These become new inputs for the tradeoff model.  
```{r, eval=FALSE}
mgrid <- raster(full_path(p_agro, "ZA-grid.tif"))
msk <- raster(full_path(p_agro, "ZA-mask.tif"))
lapply(c("S", "R", "I"), function(x) { # x <- "S" 
  print(paste("Processing", x))
  DTL <- lapply(crops, function(y) {  # y <- crops[1]
    # fname <- full_path("external/base_data/", paste0(x, "-crop-yields.tif"))
    print(paste("..Processing", y))
    r <- dt_to_raster(yld_mus[[y]][[x]], CRSobj = gcs)
    r2 <- disaggregate(r, fact = 10)
    r3 <- resample(r, r2)
    r4 <- projectRaster(r3, msk)
    r4 <- mask(r4, msk)
    # plot(r4)
    valinds <- which(!is.na(values(msk)))
    DT <- as.data.table.raster(r4, xy = FALSE)[valinds, ]
    DT[, c(y) := round(get(y))]
    DT
  })
  DTdt <- do.call(cbind, DTL)
  fnm <- full_path(p_root,
                   paste0("external/data/ZA-potential-yields-", x, ".csv"))
  write.table(DTdt, file = fnm, sep = ",", col.names = TRUE, row.names = FALSE)
})
```
<a href="#top">Back to top</a>

>>>>

Based on simulated potential yields run by Di Tian. 
```{r, eval = FALSE}
library(agroEcoTradeoff)
# library(data.table)
library(lmisc)
# library(dtraster)
# devtools::install_github("PrincetonUniversity/lmisc")

p_root <- lmisc::set_base_path()
p_crop <- "~/Dropbox/data/agricultural/zambia/dssat/"
p_cropmod <- "~/Dropbox/projects/rCropMod/external/ext_data/"
p_agro <- "~/Dropbox/projects/agroEcoTradeoff/external/base_data/"
p_yield <- full_path(p_root, "external/input_devel/yield")

@@

prj <- paste0("+proj=aea +lat_1=20 +lat_2=-23 +lat_0=0 +lon_0=25 +x_0=0 +y_0=0",
              " +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs")
gcs <- "+proj=longlat +datum=WGS84"
plot(dt_to_raster(IDr[, .(x, y, as.factor(Zone))], CRS(prj)))

@@

# Take average of mean yields across the different cultivar types. 
# This will give 1 set of yields for each of the three management scenarios
# Subsistence, rainfed commercial, irrigated
# The same approach can be used to estimate the average of the 10th percentile 
# across cultivars, or median, or 90th, etc.

# fill in yield at edges
yield_fix <- function(x = r[[1]], w, na.rm = TRUE) {
  r <- focal(x, w = w, fun = mean, na.rm = na.rm)
  rmsk <- (!is.na(r) & is.na(x)) * r
  x[is.na(x)] <- 0
  rfix <- x + rmsk  # add back in edge bits
}

# ra
yld_rl <- lapply(crops, function(x) {  # x <- crops[[1]]
  yr <- lapply(c("S", "R", "I"), function(y) {  #y <- "S"
    ylds <- yld_rasts[[x]]
    nms <- names(ylds)
    cnms <- nms[grep(paste0("y.*._", y), nms)]
    r <- dt_to_raster(ylds[, c("x", "y", cnms), with = FALSE], CRSobj = gcs)
    w <- matrix(ncol = 3, nrow = 3, rep(1, 9))
    rfoc <- sapply(1:nlayers(r), function(i) rfoc <- yield_fix(r[[i]], w = w))
    names(rfoc) <- names(r)
    rs <- stack(rfoc)
    rs
  })
  named_out(yr, c("S", "R", "I"))
})
names(yld_rl) <- crops

for(i in 1:length(yld_rl)) {
  rl <- yld_rl[[i]]
  for(j in 1:length(rl)) {
    fnm <- full_path(p_yield, paste0(crops[i], "_", names(rl)[j], "_10K.tif"))
    writeRaster(rl[[j]], filename = fnm)
  }
}
```
<a href="#top">Back to top</a>

## How to make 1 km grids/data.tables

This provides the methods for taking 10 km grids, averaging them across cultivars within management treatments, and then reseampling to 1 km grids. This is approximately the approach that will be used to make inputs for the tradeoff model. Other methods to explore include blending different types of management practice, e.g. X% of each cell is irrigated, Y% is rainfed commercial, Z% is subsistence. 
```{r, eval=FALSE}
yld_mus <- lapply(crops, function(x) {  # x <- crops[[1]]
  ymu <- lapply(c("S", "R", "I"), function(y) {  #y <- "S"
    cnms <- names(yld_rasts[[x]])[grep(paste0("mu_", y), names(yld_rasts[[x]]))]
    ylds <- copy(yld_rasts[[x]][, c("x", "y", cnms), with = FALSE])
    ylds[, c(x) := round(rowMeans(.SD)), .SDcols = cnms]
    ylds[, c(cnms) := NULL]
    ylds
  })
  named_out(ymu, c("S", "R", "I"))
})
names(yld_mus) <- crops
plot(dt_to_raster(yld_mus[[2]]$R, CRSobj = gcs))

# 1 km resample
mgrid <- raster(full_path(p_agro, "ZA-grid.tif"))
msk <- raster(full_path(p_agro, "ZA-mask.tif"))
lapply(c("S", "R", "I"), function(x) { # x <- "S" 
  print(paste("Processing", x))
  DTL <- lapply(crops, function(y) {  # y <- crops[1]
    # fname <- full_path("external/base_data/", paste0(x, "-crop-yields.tif"))
    print(paste("..Processing", y))
    r <- dt_to_raster(yld_mus[[y]][[x]], CRSobj = gcs)
    r2 <- disaggregate(r, fact = 10)
    r3 <- resample(r, r2)
    r4 <- projectRaster(r3, msk)
    r4 <- mask(r4, msk)
    # plot(r4)
    valinds <- which(!is.na(values(msk)))
    DT <- as.data.table.raster(r4, xy = FALSE)[valinds, ]
    DT[, c(y) := round(get(y))]
    DT
  })
  DTdt <- do.call(cbind, DTL)
  fnm <- full_path(p_root,
                   paste0("external/data/ZA-potential-yields-", x, ".csv"))
  write.table(DTdt, file = fnm, sep = ",", col.names = TRUE, row.names = FALSE)
})
```
<a href="#top">Back to top</a>

## Resulting model inputs

`maize_S|R|I_10K.tif` - 10 km maize grids for different management
`soybean_S|R|I_10K.tif` - 10 km soy grids for different management

These will have to go through intermediate, and perhaps on the fly, processing in batch mode to represent different yield scenarios.

### 2016-01-20 Rmd/to-do.Rmd
Many updates as getting ready to assemble and mask inputs

# make an html table
# http://r-norberg.blogspot.com/2013/06/generating-tables-using-pander-knitr.html
tabl <- cbind(
  "Item" = c("Plausible Scenario", 
             "Gridded yields",
             "Gridded yields",
             "Upgrade soils", 
             "Filter terrain", 
             "Biodiversity impacts", 
             "Impacts weighting (per Tim)", 
             "Work in economics", 
             "Explore econ versus enviro goals", 
             "Better cropland map, yield estimates", 
             "Updated carbon layers"), 
  "Notes" = c("Single production to follow (Alastair)", 
              "Exact method for variability and production zones, including inability to reach potential yields", 
              "Run with improved soils maps", 
              "With ILUA database (and Nate's help)", 
              "Removable unfarmable areas, add new supporting logic", 
              "Habitat rarity/threatenedness", 
              "Weight carbon and biodiversity equally", 
              "Estimate profitability per pixel. Either input modification or code modification", 
              "See where map overlaps are greatest, most divergent", 
              "Upgrade all maps to SERVIR landcover, and rebase yield estimates on that", "Baccini vegetation carbon + ISRIC grids"),
  "Doing" = c("D", "D", "U", "U", "D", "D", "D", "L", "D", "D", "F")
)
print(xtable::xtable(tabl), align = rep("c", dim(table)[2] + 1), type = "html", 
      include.rownames = FALSE)
```

>>>>

# make an html table
# http://r-norberg.blogspot.com/2013/06/generating-tables-using-pander-knitr.html
tabl <- cbind(
  "Item" = c("Plausible Scenario", 
             "Gridded yields",
             "Gridded yields",
             "Upgrade soils", 
             "Filter terrain", 
             "Biodiversity impacts", 
             "Impacts weighting (per Tim)", 
             "Work in economics", 
             "Explore econ versus enviro goals", 
             "Better cropland map, yield estimates", 
             "Updated carbon layers"), 
  "Notes" = c("Single production to follow (Alastair)", 
              "Exact method for variability and production zones, including inability to reach potential yields", 
              "Run with improved soils maps", 
              "With ILUA database (and Nate's help)", 
              "Removable unfarmable areas, add new supporting logic", 
              "Habitat rarity/threatenedness", 
              "Weight carbon and biodiversity equally", 
              "Estimate profitability per pixel. Either input modification or code modification", 
              "See where map overlaps are greatest, most divergent", 
              "Upgrade all maps to SERVIR landcover, and rebase yield estimates on that", "Baccini vegetation carbon + ISRIC grids"),
  "Doing" = c("D", "D", "U", "U", "D", "D", "D", "L", "D", "F*", "F")
)
print(xtable::xtable(tabl), align = rep("c", dim(table)[2] + 1), type = "html", 
      include.rownames = FALSE)
```

*Just using total production estimates, which will not be mapped for now. These will be basis for estimating production targets.
